Measurement of deeply virtual Compton scattering off Helium-4 with CLAS at Jefferson Lab

### 2020-10-09 eg6-letters/long-paper/prc-dvcshelium.tex
Finish material for Ad Hoc answer on long paper

\documentclass{article}
\usepackage[left=3.5cm,right=2.5cm,top=2cm,bottom=2cm,includefoot,includehead,headheight=15pt]{geometry}
\usepackage{lineno}
%\documentclass[aps,prc,preprint,superscriptaddress]{revtex4}
%\usepackage{amsmath,amssymb}             % AMS Math
%\usepackage[francais]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern,textcomp}
\usepackage{setspace}
\usepackage{microtype}
\usepackage{epigraph}
\usepackage{natbib}
%\usepackage[scaled]{helvet}
%\usepackage[pagebackref,hyperindex=true]{hyperref}
%\usepackage{pdfpages}
\usepackage{graphicx}
\usepackage{array}
\usepackage{amsmath}

@@

Since, DVCS is a 
process selected using tight exclusivity constrains, some of the initial and final-state effects are
automatically mitigated. Selection criterion on missing energy and momentum are performed,
constraining the range of initial Fermi motion and final interactions possible. However, no theoretical
calculation is available to correct for the reminder of these effects yet. Since, modern calculations exist 
for such effects in DIS \cite{Cosyn:2017ekf}, we can expect them to be extended to the DVCS 
process as more data becomes available. Another avenue of progress
on this topic will be the use of experimental techniques like tagging. This process
can help to control both initial and final state effects by detecting the nuclear remnant.
In the tagged process the target breaks in two providing directly the initial state
of the struck nucleon, while measured backward nuclear fragments limit significantly the
impact of final state effects.

@@

@@

\section{Table of results with kinematic information}
\label{sec:fullresults}
%TODO Tables to be checked

\begin{table}[!h]
   \begin{center}
      \begin{tabular}{||l|l|l|l|l||}
         \hline
 $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
         \hline
  1.143 & 0.136 & 0.096 & 24.3  &  0.1327 $\pm$ 0.1088 $\pm$ 0.0257 \\ 
  1.143 & 0.136 & 0.096 & 61.1  &  0.3210 $\pm$ 0.0932 $\pm$ 0.0188 \\ 
  1.143 & 0.136 & 0.096 & 98.9  &  0.3709 $\pm$ 0.1026 $\pm$ 0.0403 \\ 
  1.143 & 0.136 & 0.096 & 140.9 &  0.2452 $\pm$ 0.1517 $\pm$ 0.0267 \\ 
  1.143 & 0.136 & 0.096 & 178.4 &  0.0225 $\pm$ 0.1632 $\pm$ 0.0278 \\ 
  1.143 & 0.136 & 0.096 & 219.1 & -0.0526 $\pm$ 0.1475 $\pm$ 0.0248 \\ 
  1.143 & 0.136 & 0.096 & 262.9 & -0.2642 $\pm$ 0.1196 $\pm$ 0.0389 \\ 
  1.143 & 0.136 & 0.096 & 301.9 & -0.1761 $\pm$ 0.0968 $\pm$ 0.0263 \\ 
  1.143 & 0.136 & 0.096 & 337.7 & -0.2791 $\pm$ 0.1047 $\pm$ 0.0343 \\ 
  \hline                                                                                                           
  1.423 & 0.172 & 0.099 & 21.1  &  0.1917 $\pm$ 0.0892 $\pm$ 0.0267 \\ 
  1.423 & 0.172 & 0.099 & 56.6  &  0.2819 $\pm$ 0.0866 $\pm$ 0.0250 \\ 
  1.423 & 0.172 & 0.099 & 96.9  &  0.4855 $\pm$ 0.1291 $\pm$ 0.0426 \\ 
  1.423 & 0.172 & 0.099 & 139.9 &  0.0996 $\pm$ 0.1679 $\pm$ 0.0250 \\ 
  1.423 & 0.172 & 0.099 & 180.3 &  0.1458 $\pm$ 0.1906 $\pm$ 0.0302 \\ 
  1.423 & 0.172 & 0.099 & 218.7 & -0.1109 $\pm$ 0.1853 $\pm$ 0.0344 \\ 
  1.423 & 0.172 & 0.099 & 263.1 & -0.3516 $\pm$ 0.1371 $\pm$ 0.0366 \\ 
  1.423 & 0.172 & 0.099 & 302.2 & -0.4141 $\pm$ 0.0842 $\pm$ 0.0383 \\ 
  1.423 & 0.172 & 0.099 & 338.2 & -0.2786 $\pm$ 0.0836 $\pm$ 0.0261 \\ 
  \hline                                                                                                           
  1.902 & 0.224 & 0.107 & 21.4  &  0.1803 $\pm$ 0.0805 $\pm$ 0.0234 \\ 
  1.902 & 0.224 & 0.107 & 57.2  &  0.3501 $\pm$ 0.0824 $\pm$ 0.0185 \\ 
  1.902 & 0.224 & 0.107 & 96.2  &  0.2701 $\pm$ 0.1230 $\pm$ 0.0173 \\ 
  1.902 & 0.224 & 0.107 & 139.5 &  0.3053 $\pm$ 0.2390 $\pm$ 0.0170 \\ 
  1.902 & 0.224 & 0.107 & 178.2 &  0.1028 $\pm$ 0.2670 $\pm$ 0.0126 \\ 
  1.902 & 0.224 & 0.107 & 221.4 & -0.2118 $\pm$ 0.2147 $\pm$ 0.0152 \\ 
  1.902 & 0.224 & 0.107 & 263.3 & -0.3060 $\pm$ 0.1306 $\pm$ 0.0260 \\ 
  1.902 & 0.224 & 0.107 & 303.3 & -0.1384 $\pm$ 0.0944 $\pm$ 0.0207 \\ 
  1.902 & 0.224 & 0.107 & 338.5 & -0.1633 $\pm$ 0.0791 $\pm$ 0.0163 \\ 
         \hline \hline
      \end{tabular}
      \caption{Values of the coherent $A_{LU}$ in $Q^2$ bins from Fig. \ref{fig:CohALUphi}.}
      \label{table:Coh_Q2_BSA}
   \end{center}
\end{table}

\begin{table}[!h]
   \begin{center}
      \begin{tabular}{||l|l|l|l|l||}
         \hline
 $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
         \hline

  1.164 & 0.132 & 0.095 & 25.6  &  0.0174 $\pm$ 0.1440 $\pm$ 0.0221 \\
  1.164 & 0.132 & 0.095 & 61.6  &  0.3478 $\pm$ 0.0867 $\pm$ 0.0198 \\
  1.164 & 0.132 & 0.095 & 99.0  &  0.3808 $\pm$ 0.0948 $\pm$ 0.0408 \\
  1.164 & 0.132 & 0.095 & 141.7 &  0.2943 $\pm$ 0.1379 $\pm$ 0.0333 \\
  1.164 & 0.132 & 0.095 & 178.1 &  0.0433 $\pm$ 0.1519 $\pm$ 0.0293 \\
  1.164 & 0.132 & 0.095 & 218.5 & -0.0352 $\pm$ 0.1316 $\pm$ 0.0243 \\
  1.164 & 0.132 & 0.095 & 262.7 & -0.2771 $\pm$ 0.1050 $\pm$ 0.0372 \\
  1.164 & 0.132 & 0.095 & 300.7 & -0.2138 $\pm$ 0.0836 $\pm$ 0.0259 \\
  1.164 & 0.132 & 0.095 & 335.2 & -0.2339 $\pm$ 0.1221 $\pm$ 0.0319 \\
   \hline                                                                                                         
  1.439 & 0.17 & 0.099 &  22.9  &  0.1579 $\pm$ 0.0853 $\pm$ 0.0230 \\
  1.439 & 0.17 & 0.099 &  57.1  &  0.1733 $\pm$ 0.0880 $\pm$ 0.0195 \\
  1.439 & 0.17 & 0.099 &  96.3  &  0.2259 $\pm$ 0.1331 $\pm$ 0.0295 \\
  1.439 & 0.17 & 0.099 &  139.1 &  0.2454 $\pm$ 0.1758 $\pm$ 0.0187 \\
  1.439 & 0.17 & 0.099 &  180.1 & -0.1021 $\pm$ 0.1918 $\pm$ 0.0197 \\
  1.439 & 0.17 & 0.099 &  218.9 & -0.2876 $\pm$ 0.1909 $\pm$ 0.0270 \\
  1.439 & 0.17 & 0.099 &  263.9 & -0.2943 $\pm$ 0.1360 $\pm$ 0.0292 \\
  1.439 & 0.17 & 0.099 &  302.5 & -0.3979 $\pm$ 0.0921 $\pm$ 0.0331 \\
  1.439 & 0.17 & 0.099 &  338.1 & -0.2692 $\pm$ 0.0834 $\pm$ 0.0254 \\
   \hline                                                                                                         
  1.844 & 0.225 & 0.107 & 20.1  &  0.2626 $\pm$ 0.0755 $\pm$ 0.0248 \\
  1.844 & 0.225 & 0.107 & 55.9  &  0.4281 $\pm$ 0.0887 $\pm$ 0.0224 \\
  1.844 & 0.225 & 0.107 & 96.4  &  0.4925 $\pm$ 0.1390 $\pm$ 0.0271 \\
  1.844 & 0.225 & 0.107 & 137.7 & -0.2736 $\pm$ 0.2804 $\pm$ 0.0166 \\
  1.844 & 0.225 & 0.107 & 179.8 &  0.8470 $\pm$ 0.2497 $\pm$ 0.0204 \\
  1.844 & 0.225 & 0.107 & 224.7 & -0.0513 $\pm$ 0.2811 $\pm$ 0.0270 \\
  1.844 & 0.225 & 0.107 & 262.8 & -0.3416 $\pm$ 0.1694 $\pm$ 0.0353 \\
  1.844 & 0.225 & 0.107 & 304.5 & -0.1359 $\pm$ 0.1025 $\pm$ 0.0263 \\
  1.844 & 0.225 & 0.107 & 339.8 & -0.1658 $\pm$ 0.0770 $\pm$ 0.0175 \\

         \hline 
         \hline
      \end{tabular}
      \caption{Values of the coherent $A_{LU}$ in $x_B$ bins from Fig. \ref{fig:CohALUphi}.}
      \label{table:Coh_xB_BSA}
   \end{center}
\end{table}

\begin{table}[!h]
   \begin{center}
      \begin{tabular}{||l|l|l|l|l||}
         \hline
 $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
  \hline
  1.36 & 0.160 & 0.080  & 22.8  &  0.2378 $\pm$ 0.0928 $\pm$ 0.0263 \\
  1.36 & 0.160 & 0.080  & 57.6  &  0.3014 $\pm$ 0.0874 $\pm$ 0.0243 \\
  1.36 & 0.160 & 0.080  & 98.1  &  0.4896 $\pm$ 0.1118 $\pm$ 0.0394 \\
  1.36 & 0.160 & 0.080  & 139.3 &  0.1965 $\pm$ 0.1595 $\pm$ 0.0252 \\
  1.36 & 0.160 & 0.080  & 178.8 &  0.0577 $\pm$ 0.1923 $\pm$ 0.0371 \\
  1.36 & 0.160 & 0.080  & 222.6 & -0.1651 $\pm$ 0.1640 $\pm$ 0.0370 \\
  1.36 & 0.160 & 0.080  & 265.6 & -0.3467 $\pm$ 0.1339 $\pm$ 0.0403 \\
  1.36 & 0.160 & 0.080  & 300.0 & -0.2891 $\pm$ 0.0928 $\pm$ 0.0294 \\
  1.36 & 0.160 & 0.080  & 339.3 & -0.1849 $\pm$ 0.0856 $\pm$ 0.0281 \\
  \hline                                                                
  1.507 & 0.179 & 0.094 & 21.1  &  0.2481 $\pm$ 0.0931 $\pm$ 0.0267 \\ 
  1.507 & 0.179 & 0.094 & 56.4  &  0.3386 $\pm$ 0.0828 $\pm$ 0.0284 \\ 
  1.507 & 0.179 & 0.094 & 97.5  &  0.3467 $\pm$ 0.1156 $\pm$ 0.0307 \\ 
  1.507 & 0.179 & 0.094 & 141.9 &  0.1464 $\pm$ 0.1887 $\pm$ 0.0215 \\ 
  1.507 & 0.179 & 0.094 & 179.5 & -0.2814 $\pm$ 0.1864 $\pm$ 0.0360 \\ 
  1.507 & 0.179 & 0.094 & 218.5 &  0.2104 $\pm$ 0.1998 $\pm$ 0.0147 \\ 
  1.507 & 0.179 & 0.094 & 262.8 & -0.2399 $\pm$ 0.1280 $\pm$ 0.0283 \\ 
  1.507 & 0.179 & 0.094 & 303.5 & -0.1989 $\pm$ 0.0955 $\pm$ 0.0286 \\ 
  1.507 & 0.179 & 0.094 & 338.5 & -0.2098 $\pm$ 0.0875 $\pm$ 0.0201 \\ 
  \hline                                                                                                                 
  1.610 & 0.193 & 0.127 & 22.3  &  0.0280 $\pm$ 0.0909 $\pm$ 0.0214 \\
  1.610 & 0.193 & 0.127 & 60.7  &  0.3582 $\pm$ 0.0932 $\pm$ 0.0204 \\
  1.610 & 0.193 & 0.127 & 96.8  &  0.2559 $\pm$ 0.1269 $\pm$ 0.0313 \\
  1.610 & 0.193 & 0.127 & 139.9 &  0.2207 $\pm$ 0.1930 $\pm$ 0.0203 \\
  1.610 & 0.193 & 0.127 & 178.5 &  0.5138 $\pm$ 0.1832 $\pm$ 0.0354 \\
  1.610 & 0.193 & 0.127 & 217.5 & -0.2473 $\pm$ 0.1664 $\pm$ 0.0189 \\
  1.610 & 0.193 & 0.127 & 260.9 & -0.2919 $\pm$ 0.1295 $\pm$ 0.0327 \\
  1.610 & 0.193 & 0.127 & 303.4 & -0.2488 $\pm$ 0.0892 $\pm$ 0.0280 \\
  1.610 & 0.193 & 0.127 & 336.8 & -0.2825 $\pm$ 0.0901 $\pm$ 0.0261 \\
         \hline
         \hline
      \end{tabular}
      \caption{Values of the coherent $A_{LU}$ in $-t$ bins from Fig. \ref{fig:CohALUphi}.}
      \label{table:Coh_t_BSA}
   \end{center}
\end{table}

@@

\begin{table}[!h]
\begin{center}
\begin{tabular}{||l|l|l|l||}
\hline
 $<Q^{2}>$ & $<x_{B}>$ & $<-t>$  & $A_{LU}$(90$^{\circ}$) $\pm$ stat. $\pm$ syst.\\
 \hline 
  1.404 & 0.166 & 0.376 & 0.1369 $\pm$ 0.0223 $\pm$ 0.0136\\   
  1.889 & 0.232 & 0.415 & 0.1529 $\pm$ 0.0266 $\pm$ 0.0169\\   
  2.339 & 0.288 & 0.497 & 0.1902 $\pm$ 0.0299 $\pm$ 0.0169\\   
  3.098 & 0.379 & 0.641 & 0.1297 $\pm$ 0.0413 $\pm$ 0.0155\\   
 \hline                   
  1.449 & 0.163 & 0.374 & 0.1173 $\pm$ 0.0211 $\pm$ 0.0118\\   
  1.929 & 0.225 & 0.381 & 0.1772 $\pm$ 0.0237 $\pm$ 0.0183\\   
  2.334 & 0.283 & 0.468 & 0.1777 $\pm$ 0.0308 $\pm$ 0.0153\\   
  2.975 & 0.389 & 0.688 & 0.1603 $\pm$ 0.0480 $\pm$ 0.0144\\   
 \hline                   
  1.842 & 0.215 & 0.135 & 0.1828 $\pm$ 0.0205 $\pm$ 0.0143\\   
  2.149 & 0.257 & 0.281 & 0.1408 $\pm$ 0.0272 $\pm$ 0.0200\\   
  2.366 & 0.291 & 0.492 & 0.1371 $\pm$ 0.0290 $\pm$ 0.0244\\   
  2.447 & 0.312 & 1.089 & 0.1389 $\pm$ 0.0618 $\pm$ 0.0239\\

 \hline
 \hline
 \end{tabular}
 \caption{Values of the incoherent $A_{LU}$(90$^{\circ}$) in $Q^2$ (top block), $x_B$ (middle block), and $-t$ (bottom block) bins.}
 \label{table:InCoh_BSA_90}
 \end{center}
\end{table}

% Create the reference section using BibTeX:
%TODO
\bibliographystyle{unsrt}
\bibliography{hadro.bib}

>>>>

\documentclass{article}
\usepackage[left=3.5cm,right=2.5cm,top=2cm,bottom=2cm,includefoot,includehead,headheight=15pt]{geometry}
\usepackage{lineno}
%\documentclass[aps,prc,preprint,superscriptaddress]{revtex4}
%\usepackage{amsmath,amssymb}             % AMS Math
%\usepackage[francais]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern,textcomp}
\usepackage{setspace}
\usepackage{microtype}
\usepackage{epigraph}
\usepackage{natbib}
%\usepackage[scaled]{helvet}
%\usepackage[pagebackref,hyperindex=true]{hyperref}
%\usepackage{pdfpages}
\usepackage{graphicx}
\usepackage{array}
\usepackage{amsmath} 
\usepackage{multirow}

@@

Since, DVCS is a 
process selected using tight exclusivity constrains, some of the initial and final-state effects are
automatically mitigated. Selection criterion on missing energy and momentum are performed,
constraining the range of initial Fermi motion and final interactions possible. However, no theoretical
calculation is available to correct for the reminder of these effects yet. Modern calculations exist 
for such effects in DIS \cite{Cosyn:2017ekf} and quasi-elastic \cite{Ethier:2014bua}
and we can expect them to be extended to the DVCS 
process as more data becomes available. Another avenue of progress
on this topic will be the use of experimental techniques like tagging. This process
can help to control both initial and final state effects by detecting the nuclear remnant.
In the tagged process the target breaks in two providing directly the initial state
of the struck nucleon, while measured backward nuclear fragments limit significantly the
impact of final state effects.

@@

\bibliographystyle{unsrt}
\bibliography{hadro.bib}

@@

\section{Tables of results with kinematic information}
\label{sec:fullresults}

\begin{table}[!h]
   \begin{center}
      \begin{tabular}{|c|c|c|c|c|}
         \hline
 $\langle Q^{2} \rangle$ & $\langle x_{B} \rangle$ & $\langle -t \rangle$ & $\langle \phi \rangle$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
 (GeV$^{2}$) &           & (GeV$^{2}$) & (degree) &  \\
         \hline
        &       &       & 24    &  0.133  $\pm$ 0.109  $\pm$ 0.026  \\ 
        &       &       & 61    &  0.321  $\pm$ 0.093  $\pm$ 0.019  \\ 
        &       &       & 99    &  0.371  $\pm$ 0.103  $\pm$ 0.040  \\ 
        &       &       & 141   &  0.245  $\pm$ 0.152  $\pm$ 0.027  \\ 
  1.14  & 0.136 & 0.096 & 178   &  0.023  $\pm$ 0.163  $\pm$ 0.028  \\ 
        &       &       & 219   & -0.053  $\pm$ 0.148  $\pm$ 0.025  \\ 
        &       &       & 263   & -0.264  $\pm$ 0.120  $\pm$ 0.039  \\ 
        &       &       & 302   & -0.176  $\pm$ 0.097  $\pm$ 0.026  \\ 
        &       &       & 338   & -0.279  $\pm$ 0.105  $\pm$ 0.034  \\ 
  \hline 
        &       &       &  21   &  0.192  $\pm$ 0.089  $\pm$ 0.027  \\ 
        &       &       &  57   &  0.282  $\pm$ 0.087  $\pm$ 0.025  \\ 
        &       &       &  97   &  0.486  $\pm$ 0.129  $\pm$ 0.043  \\ 
        &       &       & 140   &  0.100  $\pm$ 0.168  $\pm$ 0.025  \\ 
  1.42  & 0.172 & 0.099 & 180   &  0.146  $\pm$ 0.191  $\pm$ 0.030  \\ 
        &       &       & 219   & -0.111  $\pm$ 0.185  $\pm$ 0.034  \\ 
        &       &       & 263   & -0.352  $\pm$ 0.137  $\pm$ 0.037  \\ 
        &       &       & 302   & -0.414  $\pm$ 0.084  $\pm$ 0.038  \\ 
        &       &       & 338   & -0.279  $\pm$ 0.084  $\pm$ 0.026  \\ 
  \hline 
        &       &       &  21.4 &  0.180  $\pm$ 0.081  $\pm$ 0.023  \\ 
        &       &       &  57.2 &  0.350  $\pm$ 0.082  $\pm$ 0.019  \\ 
        &       &       &  96.2 &  0.270  $\pm$ 0.123  $\pm$ 0.017  \\ 
        &       &       & 139.5 &  0.305  $\pm$ 0.239  $\pm$ 0.017  \\ 
  1.90  & 0.224 & 0.107 & 178.2 &  0.103  $\pm$ 0.267  $\pm$ 0.013  \\ 
        &       &       & 221.4 & -0.212  $\pm$ 0.215  $\pm$ 0.015  \\ 
        &       &       & 263.3 & -0.306  $\pm$ 0.131  $\pm$ 0.026  \\ 
        &       &       & 303.3 & -0.138  $\pm$ 0.094  $\pm$ 0.021  \\ 
        &       &       & 338.5 & -0.163  $\pm$ 0.079  $\pm$ 0.016  \\ 
         \hline 
      \end{tabular}
      \caption{Values of the coherent $A_{LU}$ in $Q^2$ bins from Fig. \ref{fig:CohALUphi}.}
      \label{table:Coh_Q2_BSA}
   \end{center}
\end{table}

\begin{table}[!h]
   \begin{center}
      \begin{tabular}{|c|c|c|c|c|}
         \hline
 $\langle Q^{2} \rangle$ & $\langle x_{B} \rangle$ & $\langle -t \rangle$ & $\langle \phi \rangle$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
 (GeV$^{2}$) &           & (GeV$^{2}$) & (degree) &  \\
         \hline

        &       &       &  26   &  0.017  $\pm$ 0.144  $\pm$ 0.022  \\
        &       &       &  62   &  0.348  $\pm$ 0.087  $\pm$ 0.020  \\
        &       &       &  99   &  0.381  $\pm$ 0.095  $\pm$ 0.041  \\
        &       &       & 142   &  0.294  $\pm$ 0.138  $\pm$ 0.033  \\
  1.16  & 0.132 & 0.095 & 178   &  0.043  $\pm$ 0.152  $\pm$ 0.029  \\
        &       &       & 219   & -0.035  $\pm$ 0.132  $\pm$ 0.024  \\
        &       &       & 263   & -0.277  $\pm$ 0.105  $\pm$ 0.037  \\
        &       &       & 301   & -0.214  $\pm$ 0.084  $\pm$ 0.026  \\
        &       &       & 335   & -0.234  $\pm$ 0.122  $\pm$ 0.032  \\
   \hline 
        &       &       &   23  &  0.158  $\pm$ 0.085  $\pm$ 0.023  \\
        &       &       &   57  &  0.173  $\pm$ 0.088  $\pm$ 0.020  \\
        &       &       &   96  &  0.226  $\pm$ 0.133  $\pm$ 0.030  \\
        &       &       &  139  &  0.245  $\pm$ 0.176  $\pm$ 0.019  \\
  1.44  & 0.170 & 0.099 &  180  & -0.102  $\pm$ 0.192  $\pm$ 0.020  \\
        &       &       &  219  & -0.288  $\pm$ 0.191  $\pm$ 0.027  \\
        &       &       &  264  & -0.294  $\pm$ 0.136  $\pm$ 0.029  \\
        &       &       &  303  & -0.398  $\pm$ 0.092  $\pm$ 0.033  \\
        &       &       &  338  & -0.269  $\pm$ 0.083  $\pm$ 0.025  \\
   \hline 
        &       &       &  20   &  0.263  $\pm$ 0.076  $\pm$ 0.025  \\
        &       &       &  56   &  0.428  $\pm$ 0.089  $\pm$ 0.022  \\
        &       &       &  96   &  0.493  $\pm$ 0.139  $\pm$ 0.027  \\
        &       &       & 138   & -0.274  $\pm$ 0.280  $\pm$ 0.017  \\
  1.84  & 0.225 & 0.107 & 180   &  0.847  $\pm$ 0.250  $\pm$ 0.020  \\
        &       &       & 225   & -0.051  $\pm$ 0.281  $\pm$ 0.027  \\
        &       &       & 263   & -0.342  $\pm$ 0.169  $\pm$ 0.035  \\
        &       &       & 305   & -0.136  $\pm$ 0.103  $\pm$ 0.026  \\
        &       &       & 340   & -0.166  $\pm$ 0.077  $\pm$ 0.018  \\
         \hline
      \end{tabular}
      \caption{Values of the coherent $A_{LU}$ in $x_B$ bins from Fig. \ref{fig:CohALUphi}.}
      \label{table:Coh_xB_BSA}
   \end{center}
\end{table}

\begin{table}[!h]
   \begin{center}
      \begin{tabular}{|c|c|c|c|c|}
         \hline
 $\langle Q^{2} \rangle$ & $\langle x_{B} \rangle$ & $\langle -t \rangle$ & $\langle \phi \rangle$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
 (GeV$^{2}$) &           & (GeV$^{2}$) & (degree) &  \\
  \hline
        &       &       &  23   &  0.238  $\pm$ 0.093  $\pm$ 0.026  \\
        &       &       &  58   &  0.301  $\pm$ 0.087  $\pm$ 0.024  \\
        &       &       &  98   &  0.490  $\pm$ 0.112  $\pm$ 0.039  \\
        &       &       & 139   &  0.197  $\pm$ 0.160  $\pm$ 0.025  \\
  1.36  & 0.160 & 0.080 & 179   &  0.058  $\pm$ 0.192  $\pm$ 0.037  \\
        &       &       & 223   & -0.165  $\pm$ 0.164  $\pm$ 0.037  \\
        &       &       & 266   & -0.347  $\pm$ 0.134  $\pm$ 0.040  \\
        &       &       & 300   & -0.289  $\pm$ 0.093  $\pm$ 0.029  \\
        &       &       & 339   & -0.185  $\pm$ 0.086  $\pm$ 0.028  \\
  \hline 
        &       &       &  21   &  0.248  $\pm$ 0.093  $\pm$ 0.027  \\ 
        &       &       &  56   &  0.339  $\pm$ 0.083  $\pm$ 0.028  \\ 
        &       &       &  98   &  0.347  $\pm$ 0.116  $\pm$ 0.031  \\ 
        &       &       & 142   &  0.146  $\pm$ 0.189  $\pm$ 0.022  \\ 
  1.51  & 0.179 & 0.094 & 180   & -0.281  $\pm$ 0.186  $\pm$ 0.036  \\ 
        &       &       & 219   &  0.210  $\pm$ 0.200  $\pm$ 0.015  \\ 
        &       &       & 263   & -0.240  $\pm$ 0.128  $\pm$ 0.028  \\ 
        &       &       & 304   & -0.199  $\pm$ 0.096  $\pm$ 0.029  \\ 
        &       &       & 339   & -0.210  $\pm$ 0.088  $\pm$ 0.020  \\ 
  \hline
        &       &       &  22   &  0.028  $\pm$ 0.091  $\pm$ 0.021  \\
        &       &       &  61   &  0.358  $\pm$ 0.093  $\pm$ 0.020  \\
        &       &       &  97   &  0.256  $\pm$ 0.127  $\pm$ 0.031  \\
        &       &       & 140   &  0.221  $\pm$ 0.193  $\pm$ 0.020  \\
  1.61  & 0.193 & 0.127 & 179   &  0.514  $\pm$ 0.183  $\pm$ 0.035  \\
        &       &       & 218   & -0.247  $\pm$ 0.166  $\pm$ 0.019  \\
        &       &       & 261   & -0.292  $\pm$ 0.130  $\pm$ 0.033  \\
        &       &       & 303   & -0.249  $\pm$ 0.089  $\pm$ 0.028  \\
        &       &       & 337   & -0.283  $\pm$ 0.090  $\pm$ 0.026  \\
         \hline
      \end{tabular}
      \caption{Values of the coherent $A_{LU}$ in $-t$ bins from Fig. \ref{fig:CohALUphi}.}
      \label{table:Coh_t_BSA}
   \end{center}
\end{table}

@@

\begin{table}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
 $\langle Q^{2} \rangle$ & $\langle x_{B} \rangle$ & $\langle -t \rangle$  & $A_{LU}$(90$^{\circ}$) $\pm$ stat. $\pm$ syst.\\
 (GeV$^{2}$) &           & (GeV$^{2}$) &  \\
 \hline 
  1.40  & 0.166 & 0.376 & 0.137  $\pm$ 0.022  $\pm$ 0.014 \\   
  1.89  & 0.232 & 0.415 & 0.153  $\pm$ 0.027  $\pm$ 0.017 \\   
  2.34  & 0.288 & 0.497 & 0.190  $\pm$ 0.030  $\pm$ 0.017 \\   
  3.10  & 0.379 & 0.641 & 0.130  $\pm$ 0.041  $\pm$ 0.016 \\   
 \hline 
  1.45  & 0.163 & 0.374 & 0.117  $\pm$ 0.021  $\pm$ 0.012 \\   
  1.93  & 0.225 & 0.381 & 0.177  $\pm$ 0.024  $\pm$ 0.018 \\   
  2.33  & 0.283 & 0.468 & 0.178  $\pm$ 0.031  $\pm$ 0.015 \\   
  2.98  & 0.389 & 0.688 & 0.160  $\pm$ 0.048  $\pm$ 0.014 \\   
 \hline 
  1.84  & 0.215 & 0.135 & 0.183  $\pm$ 0.021  $\pm$ 0.014 \\   
  2.15  & 0.257 & 0.281 & 0.141  $\pm$ 0.027  $\pm$ 0.020 \\   
  2.37  & 0.291 & 0.492 & 0.137  $\pm$ 0.029  $\pm$ 0.024 \\   
  2.45  & 0.312 & 1.089 & 0.139  $\pm$ 0.062  $\pm$ 0.024 \\   
 \hline
 \end{tabular}
 \caption{Values of the incoherent $A_{LU}$(90$^{\circ}$) in $Q^2$ (top block), $x_B$ (middle block), and $-t$ (bottom block) bins.}
 \label{table:InCoh_BSA_90}
 \end{center}
\end{table}
